Progress Report for CSS 586: \\ Modeling Latent Patterns in Music

### 2021-04-19 papers/progress/alex/progress-alex.tex
save report

The major advantage of working with the symbolic representation of music is that
it is of far lower dimensionality than the raw audio waveforms of a recorded
performance,

>>>>

A major advantage of working with the symbolic representation of music is that
it is of far lower dimensionality than the raw audio waveforms of a recorded
performance, which makes it less computationally expensive. However, there are
many aspects of musical performance that are not captured by a symbolic
representation, so the expressiveness of symbolic generative models is
constrained \cite{manzelli_conditioning_2018}.
